% Standard preamble
\documentclass[11pt]{article}
\usepackage{geometry, hyperref, sectsty}
\usepackage[resetlabels]{multibib}
\newcites{shortlist,subs}
{Selected Publications (from 17 total),Under Review}

\makeatletter
\def\@biblabel#1{}
\makeatother

%pagestyle
% US STYLE
\geometry{
letterpaper,
total={7in,9.5in},
left=0.75in,
top=0.75in}
% EUROPEAN STYLE
%\geometry
%{
% a4paper,
% total={170mm,280mm},
% left=20mm,
% top=10mm,
%}
\parindent = 0pt
\parskip = 6pt
\sectionfont{\fontsize{13.2}{6}\selectfont}

% Define bullet
\def\bullitem{\par\hangindent=15pt \hangafter=1
\noindent\hbox to 20pt{\hfil$\bullet$\hfil}\ignorespaces}

\begin{document}

% Header/Contact Info
{\large \textbf{Tyler H.\ Chang}}

\begin{tabular}{ll}
   Argonne National Laboratory
      & Email: \href{mailto:tchang@anl.gov}{tchang@anl.gov}\\
   Mathematics and Computer Science Division
      & Website: \url{http://thchang.github.io}\\
   9700 S.\ Cass Ave.\ Bldg.\ 240, Lemont, IL 60439
      & GitHub: \url{http://github.com/thchang} \\
\end{tabular}

% Begin document
%\section*{Primary Interests}
%
%Optimization, machine learning, algorithms, and parallel computing.

\section*{Education}

Ph.D., May 2020, Computer Science,
Virginia Polytechnic Institute \& State University
(Virginia Tech)

\medskip

B.S., May 2016, Computer Science \& Mathematics,
Virginia Wesleyan University, \textit{Summa Cum Laude}

\section*{Research Experience}

\hangafter=1
\hangindent=0.3in
(June, 2020 -- Present)
\textbf{Postdoctoral Appointee: Argonne National Lab},
Mathematics and Computer Science (MCS) Division.
\bullitem R\&D in multiobjective optimization, parallel computing, and
scientific software.
\bullitem Member of FASTMATH: A SciDAC institute spanning
5 national labs and 5 universities.

\medskip

\hangafter=1
\hangindent=0.3in
(Aug, 2016 -- May, 2020)
\textbf{Cunningham Fellow: Virginia Tech},
Dept.\ of Computer Science.
\bullitem
R\&D in numerical analysis, math software,
algorithms, parallel computing, and data science.
\bullitem
Math \& Algorithms team in VarSys: A NSF funded study of
HPC performance variability.

\medskip

\hangafter=1
\hangindent=0.3in
(June, 2019 -- Dec, 2019)
\textbf{SCGSR Awardee: Argonne National Lab}, MCS Division.
\bullitem
R\&D in multiobjective optimization, funded via ORAU/ORISE
(see awards for details).

\medskip

\hangafter=1
\hangindent=0.3in
(Feb -- Aug, 2016)
\textbf{Research Assistant: Old Dominion University},
Dept.\ of Computer Science.
\bullitem
R\&D in GPU computing and parallelization of NASA's FUN3D CFD kernel on
NVIDIA GPUs.

\medskip

%\hangafter=1
%\hangindent=0.3in
%(Summer 2014, Winter 2014, Summer 2015, \& Winter 2015)
%\textbf{Intern: US Army Research Labs}, 
%Computational Science Division (CSD) and Guidance Technology Branch (GTB).
%\bullitem
%CSD --- R\&D in autonomous driving (Summer 2015) \&
%virtual reality (Winter 2015).
%\bullitem
%GTB --- R\&D in computer vision (Summer 2014) \& embedded systems (Winter 2014).
%
%\medskip

\section*{Awards}

\textbf{Cunningham Doctoral Fellow} (2016--2020).
The 
\href{https://graduateschool.vt.edu/funding/types-of-funding/funding-sponsored-by-the-graduate-school/cunningham-doctoral-assistantships.html}
{Cunningham doctoral fellowship} is a Virginia Tech graduate school wide
award, guaranteeing 4 years of research funding.

\textbf{Davenport Leadership Fellow} (2016--17 \& 2019--20).
The Davenport leadership fellowship is a supplemental award given by
Virginia Tech, College of Engineering on a per-year basis.

\textbf{DOE SCGSR Awardee} (2019).
One of 70 proposals funded by the United States Dept.\ of Energy,
Office of Science Graduate Student Research program, during the
\href{https://www.energy.gov/articles/doe-s-science-graduate-student-research-program-selects-70-students-pursue-research-doe}{2018, 2nd call for proposals}.

\textbf{Pratt Fellow} (2017--18 \& 2018--19).
The Pratt fellowship is a supplemental award given by
Virginia Tech, College of Engineering on a per-year basis.

\section*{Publicly Available Software}

\textbf{DELAUNAYSPARSE} is a software package for computing the Delaunay
interpolant in medium to high dimensions.
Both serial and parallel drivers are available with interfaces in
\texttt{Fortran},
\texttt{C/C++},
\texttt{Python 3.6+},
and command line.
Download: \url{https://vtopt.github.io/DelaunaySparse}.

\textbf{QAML} is a \texttt{Python} package for embedding polynomial sum of
squares minimization problems on the D-Wave quantum annealer.
Download: \url{https://github.com/tchlux/qaml}.

\section*{Pending Software}

\textbf{VTMOP} is a solver and framework for computationally
expensive blackbox multiobjective optimization problems with continuous
variables and 2+ objectives.
Written in \texttt{Fortran}; a \texttt{Python} interface is also available
through \texttt{libEnsemble} (\url{https://github.com/libensemble/libensemble}).

\nociteshortlist{*}
\nocitesubs{*}
\bibliographystyleshortlist{cv}
\bibliographystylesubs{cv}
\bibliographyshortlist{shortlist}
\bibliographysubs{subs}

\section*{Professional Activities}

\textbf{Referee:} For
Journal of Machine Learning Research (2019);
IEEE SoutheastCon (2018 -- 2020).

\textbf{Session Chair:}
SIAM Conference on Computational Science and Engineering (2021);
SIAM Conference on Optimization (2021);
IEEE SoutheastCon (2018).

\textbf{Counselor / Founding Member:} Virginia Tech CS Graduate Counsel 
(Fall, 2017 -- Fall, 2019).
Organizing professional and social events for
current and prospective graduate students.

\end{document} 
