% Standard preamble
\documentclass[11pt]{article}
\usepackage{geometry, hyperref}
\usepackage[resetlabels]{multibib}
\newcites{pubs,inps,subs,talks}
{Peer-Reviewed Publications,In Press,Under Review,Contributed Talks}

\makeatletter
\def\@biblabel#1{}
\makeatother

%pagestyle
% US STYLE
\geometry{
letterpaper,
total={7in,9.5in},
left=0.75in,
top=0.75in}
% EUROPEAN STYLE
%\geometry
%{
% a4paper,
% total={170mm,280mm},
% left=20mm,
% top=10mm,
%}
\parindent = 0pt
\parskip = 6pt

% Define bullet
\def\bullitem{\par\hangindent=15pt \hangafter=1
\noindent\hbox to 20pt{\hfil$\bullet$\hfil}\ignorespaces}

\begin{document}

% Header/Contact Info
{\Large \textbf{Tyler H.\ Chang}}

\begin{tabular}{ll}
   Argonne National Laboratory & Email: tchang@anl.gov\\
   Mathematics and Computer Science Division & Phone: TBD\\
   9700 S.\ Cass Ave.\ Bldg.\ 240, Lemont, IL 60439
      & Web: \url{http://people.cs.vt.edu/~thchang} \\
\end{tabular}

% Begin document
\section*{Research Interests}

Numerical optimization, approximation theory, mathematical software,
algorithms, and parallel computing for applications in scientific computing,
data science, and engineering design.

\section*{Education}

\begin{tabular}{lcl}
Ph.D. & 2020 & Computer Science and Applications, Virginia Tech\\
& & Thesis: 
\href{http://hdl.handle.net/10919/98915}
{\it Mathematical Software for Multiobjective Optimization Problems}\\
& & Advisor: Layne T.\ Watson\\
& \\
B.S. & 2016 & Computer Science \& Mathematics,
Virginia Wesleyan University, \textit{Summa Cum Laude}\\
\end{tabular}

\section*{Research Experience}

(June, 2020 -- Present)\\
\textbf{Postdoctoral Appointee: Argonne National Lab},
Mathematics \& Computer Science (MCS) Division.
\bullitem R\&D in multiobjective optimization for scientific applications.

\medskip

(Aug, 2016 -- May, 2020)\\
\textbf{Cunningham Doctoral Fellow: Virginia Tech}, Dept.\ of Computer Science.
\bullitem
R\&D in numerical analysis, mathematical software, parallel computing,
algorithms, and data science.
\bullitem
Math \& Algorithms team on the VarSys project: a NSF funded study of
HPC performance variability.

\medskip

(June -- Dec, 2019)\\
\textbf{DOE SCGSR Awardee: Argonne National Lab}, MCS
Division (see awards).
\bullitem
R\&D of multiobjective optimization software for computationally expensive
blackbox problems.

\medskip

(Feb -- Aug, 2016)\\
\textbf{Research Assistant: Old Dominion University},
Dept.\ of Computer Science.
\bullitem
R\&D in GPU computing and parallelization of NASA's FUN3D CFD kernel on
NVIDIA GPUs.

\medskip

(Summer 2014, Winter 2014, Summer 2015, \& Winter 2015)\\
\textbf{Intern: US Army Research Labs}, Guidance Tech.\ Branch (GTB)
\& Computational Sci.\ Div.\ (CSD).
\bullitem
CSD --- R\&D in autonomous driving (Summer 2015) \&
virtual reality (Winter 2015).
\bullitem
GTB --- R\&D in computer vision (Summer 2014) \& embedded systems (Winter 2014).

\section*{Awards}

\textbf{Cunningham Doctoral Fellow} (2016--2020).
The 
\href{https://graduateschool.vt.edu/funding/types-of-funding/funding-sponsored-by-the-graduate-school/cunningham-doctoral-assistantships.html}
{Cunningham doctoral fellowship} is a Virginia Tech graduate school wide
award, guaranteeing 4 years of research funding.

\textbf{Davenport Leadership Fellow} (2016--17 \& 2019--20).
The Davenport leadership fellowship is a supplemental award given by
the College of Engineering on a per-year basis.

\textbf{DOE SCGSR Awardee} (2019).
One of 70 proposals funded by the United States Dept.\ of Energy,
Office of Science Graduate Student Research program, during the
\href{https://www.energy.gov/articles/doe-s-science-graduate-student-research-program-selects-70-students-pursue-research-doe}{2018, 2nd call for proposals}.
Award based on peer review of proposal by scientific experts.

\textbf{Pratt Fellow} (2017--18 \& 2018--19).
The Pratt fellowship is a supplemental award given by
the College of Engineering on a per-year basis.

\textbf{Outstanding Student in Computer Science and Mathematics} (2016).
During Spring Convocation, one or two outstanding from each department
are recognized by Virginia Wesleyan University.

\nocitepubs{*}
\nociteinps{*}
\nocitesubs{*}
\nocitetalks{*}
\bibliographystylepubs{cv}
\bibliographystyleinps{cv}
\bibliographystylesubs{cv}
\bibliographystyletalks{cv}
\bibliographypubs{pubs}
\bibliographyinps{inps}
\bibliographysubs{subs}
\bibliographytalks{talks}

\section*{Professional Activities}

\textbf{Referee:} For
Journal of Machine Learning Research (2019) and
IEEE SoutheastCon (2018 -- 2020).

\textbf{Session Vice-Chair:} IEEE SoutheastCon (2018).

\textbf{Membership:} ACM (2015 -- Present), SIAM (2016 -- Present), and
SCS (2020 -- Present).

\textbf{Counselor / Founding Member:} Virginia Tech CS Graduate Counsel 
(Fall, 2017 -- Fall, 2019).
Organizing professional, social, and informative events for
current and prospective graduate students.

\section*{Teaching Experience}

(Spring, 2020)
\textbf{Instructor: Virginia Tech}, Dept.\ of Computer Science.
\bullitem
Instructor for {\it CS 3114: Data Structures and Algorithms}.

\medskip

(Spring, 2013 -- Fall, 2015)
\textbf{Subject Tutor: Virginia Wesleyan University}, Learning Center.
\bullitem
Subject tutor for undergraduate courses in calculus, computer science, and
statistics.

\end{document} 
